On The Impact of Atoms of Confusion in JavaScript Code

### 2021-10-25 2_Background.tex
submitted version

Santos and Gerosa~\cite{Santos:2018:ICP} analyze the impact of eleven coding practices on program readability. However, most of the practices analyzed in their study relate to code formatting, instead of language constructs or idioms that might introduce misunderstanding. In addition, the study participants did not have to perform comprehension tasks. We borrow from their research the methodology for collecting the practitioner's opinion about code snippets. Indeed, such a methodology is a well-known approach for comparing developers' preferences among pairs of code snippets (e.g., the work of M. Arab about the effect of code comments and documentation already uses this approach~\cite{arab:sigplan}).

>>>>

%Santos and Gerosa~\cite{Santos:2018:ICP} analyze the impact of eleven coding practices on program readability. However, most of the practices analyzed in their study relate to code formatting, instead of language constructs or idioms that might introduce misunderstanding. In addition, the study participants did not have to perform comprehension tasks. We borrow from their research the methodology for collecting the practitioner's opinion about code snippets. Indeed, such a methodology is a well-known approach for comparing developers' preferences among pairs of code snippets (e.g., the work of M. Arab about the effect of code comments and documentation already uses this approach~\cite{arab:sigplan}).
